Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-27 paper/paper.tex
minor

The state (\texttt{\$state}) is threaded through the computation
and contains data used by inference algorithm. \texttt{\$state}
is a Clojure hash map:
\begin{lstlisting}[style=default]
(def initial-state
  "initial program state"
  {:log-weight 0.0
   :result nil
   ::mem {}
   ::store nil
   ... })
\end{lstlisting}
The full list of map entries depends on the inference
algorithm. Except for transformation of
\texttt{mem}, the memoization form, CPS transformation routines
are not aware of contents of \texttt{\$state}, do not access or
modify it directly, but rather just thread the state unmodified
through the computation. Algorithm-specific handlers of
checkpoints corresponding to the probabilistic forms
(\texttt{sample}, \texttt{observe}) modify the
state and reinject a new state into the computation.

>>>>

The state (\texttt{\$state}) is threaded through the computation
and contains data used by inference algorithms. \texttt{\$state}
is a Clojure hash map:
\begin{lstlisting}[style=default]
(def initial-state
  "initial program state"
  {:log-weight 0.0,
   :result nil,
   ::mem {},
   ::store nil,
   ... })
\end{lstlisting}
which records inference-relevant information under various keys
such as $\texttt{:log-weight}$ and $\texttt{::mem}$.
The full list of map entries depends on the inference
algorithm. Except for transformation of
\texttt{mem} (which converts a function to one with memoization), 
CPS transformation routines
are not aware of contents of \texttt{\$state}, do not access or
modify it directly, but rather just thread the state unmodified
through the computation. Algorithm-specific handlers of
checkpoints corresponding to the probabilistic forms
(\texttt{sample}, \texttt{observe}) modify the
state and reinject a new state into the computation.
